\documentclass[a4paper,8pt]{article}

% Basic packages
\usepackage{parskip} 
\usepackage{hologo}
\usepackage{color}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=.35in, bottom=.35in]{geometry}

% Tables and layout
\usepackage{tabularx}
\usepackage{supertabular}
\newcolumntype{C}{>{\centering\arraybackslash}X} 

% Lists
\usepackage{enumitem}

% Section formatting
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

% Bibliography
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

% Social icons
\usepackage{fontawesome5}

% Underline styles
\usepackage[normalem]{ulem}

% Custom section style
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{1pt}{11pt}{11pt} % Increase spacing before & after sections

% Hyperref - load last
\usepackage[unicode, colorlinks=true, urlcolor=371e77, linkcolor=371e77]{hyperref}

\begin{document}

\pagestyle{empty} 

%-------------------------
% Header with name and contact info
%-------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\color[HTML]{1C033C} \Huge{Delwin Prakash} \\[6pt]

\textcolor[HTML]{371e77}{\faEnvelope\ dev.delwin@gmail.com} $|$
\textcolor[HTML]{371e77}{\faMobile\ +91 9495356282} \\[4pt]

\textcolor[HTML]{371e77}{\underline{\href{https://github.com/delwinprakash}{\raisebox{-0.05\height}{\faGithub} github.com/delwinprakash}}} $|$
\textcolor[HTML]{371e77}{\underline{\href{https://linkedin.com/in/delwinprakash}{\raisebox{-0.05\height}{\faLinkedin} linkedin.com/in/delwinprakash}}} $|$
\textcolor[HTML]{371e77}{\underline{\href{https://x.com/prakashdelwin}{\raisebox{-0.05\height}{\faTwitter} x.com/prakashdelwin}}}
\end{tabularx}

%-------------------------
% Skills Section
%-------------------------
\section{Skills}
\color[HTML]{1C033C}\textbf{Languages:} C, Java, JavaScript, Python, Rust, Solidity, SQL, TypeScript\\[3pt]
\color[HTML]{1C033C}\textbf{Technologies \& Tools:} Anchor, AngularJS, Appwrite, Bootstrap, Ethereum, ExpressJS, Figma, Git, Github, NodeJS, MongoDB, Postman, ReactJS, React Native, Smart Contracts, Solana, Supabase, TailwindCSS, Vercel, VS Code, Web3.js

%-------------------------
% Objective Section
%-------------------------
\section{Objective}
\begin{description}[nosep, leftmargin=0.5em, itemsep=2pt]
    \item[] Computer Science student passionate about full-stack development and blockchain technology. Experienced in building scalable web/mobile applications using modern frameworks like React, Node.js, and Next.js. Eager to contribute to innovative projects in software development.
\end{description}

%-------------------------
% Work Experience Section
%-------------------------
\section{Work Experience}
\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Aoctolabs, Web3 Startup} & \color[HTML]{371e77} Oct 2024 \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Front-End Developer (Intern)}} & \\[5pt]
\multicolumn{2}{@{}X@{}}{%
    \begin{itemize}[nosep, after=\strut, leftmargin=2em, itemsep=2pt]
        \item Developed and deployed responsive user interfaces using ReactJS and Tailwind CSS, ensuring cross-device compatibility.
        \item Optimized website performance through clean code practices and modern design principles.
        \item Collaborated with team members to translate requirements into interactive features.
    \end{itemize}
}\\
\end{tabularx}

%-------------------------
% Education Section
%-------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l r@{}}
\color[HTML]{1C033C}\textbf{Government Engineering College, Wayanad} & \color[HTML]{371e77} Nov 2022 -- May 2026 (Present) \\

\color[HTML]{371e77} B.E. in Computer Science and Engineering & \color[HTML]{371e77} CGPA: 7.74 \\[3pt]

% \color[HTML]{371e77} B.E. in Computer Science and Engineering & \\[3pt]

\multicolumn{2}{@{}X@{}}{Relevant Coursework: Object Oriented Programming, Databases, Discrete Maths, Data Structures and Algorithms, Operating Systems, Computer Networks, Image Processing}
\end{tabularx}

%-------------------------
% Project Work Section
%-------------------------
\section{Project Work}
\begin{tabularx}{\linewidth}{@{}X@{}}
    \begin{itemize}[nosep, after=\strut, leftmargin=2em, itemsep=2pt]
        \item \textbf{\href{https://crates.io/crates/rusty-type}{Rusty-Type:}} Interactive typing test game in Rust using Termion, featuring real-time keystroke handling, colored feedback, dynamic timers, custom word-count modes, and a persistent high-score system. Implemented raw terminal control, cursor manipulation, multi-threaded timer logic, and efficient character-by-character rendering without external UI frameworks.

        \item \textbf{\href{https://journal-sol-one.vercel.app}{Journal.sol:}} A decentralized journaling dApp built on the Solana blockchain using Anchor and Next.js. Users can create, update, and delete journal entries, choose between public and private visibility, and have each entry stored securely on-chain.
        
        \item \textbf{\href{https://github.com/DelwinPrakash/chatapp}{ChatApp:}} Developed a cross-platform real-time chat application using React Native and Expo, leveraging Supabase for backend authentication and real-time messaging, featuring secure user sign-up/login, instant message updates, and an intuitive UI with responsive design.
        
        \item \textbf{Ecollect – Waste Management Website:} Built a full-stack waste management web application using MERN Stack, featuring user authentication, waste collection scheduling, and real-time tracking, styled with Tailwind CSS for a responsive and modern UI.
        
        % \item \textbf{\href{https://delwin.vercel.app}{Personal Portfolio Website:}} Developed a high-performance, SEO-optimized portfolio using Next.js, featuring server-side rendering (SSR), dynamic routing, and a responsive design. Integrated modern UI animations, a project showcase with filtering, all deployed on Vercel for seamless CI/CD.
    \end{itemize}
\end{tabularx}

%-------------------------
% Certificates Section
%-------------------------
\section{Certificates}
\begin{tabularx}{\linewidth}{@{}X@{}}
    \begin{itemize}[nosep, after=\strut, leftmargin=2em, itemsep=2pt]
        \item \textbf{Ethereum Learner:} Designed and deployed smart contracts using Solidity, with hands-on experience in DeFi protocols and dApp development.
        \item \textbf{Explore ML Beginner Track:} Completed the Google Explore ML Beginner Track (Certificate issued by Crowdsource by Google), gaining foundational knowledge in machine learning concepts and practical applications under the guidance of Google program managers.
    \end{itemize}
\end{tabularx}

\end{document}
